Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-10-13 04_paper/10_12_draft.Rmd
adding to hypothesis section

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```
\clearpage

@@

On the one hand, since aid is supposed to have more direct links to China's foreign policy goals, it follows that China will complement its aid giving with visible acts of diplomacy and efforts to increase the salience of aid recipients in foreign audiences. On the other hand, while aid and debt may have distinct goals, such a tidy distinction may be too simplistic. Perhaps more importantly, some of the market oriented objectives that drive China's global debt might benefit from public displays of diplomacy. On this front, recent research suggests that Beijing uses its debt to ensure access to natural resources that China lacks domestically. As noted above, @dreherEtAl2021 find that Beijing targets more of its loans in resource rich developing countries, a strategy that @dreher_banking_2022 contend is meant to guarantee access to said resources. When Beijing's policy banks provide these loans, developing country governments collateralize their oil or rare minerals, all but assuring access to these resources for Beijing since many of these countries are unable to directly repay the loans[@dreher_banking_2022].

@@

We have made the case that both state-sponsored media outreach and diplomatic visits have essential implications to sway foreign public opinion. News editors build the credibility of the news agency to transmit information around the globe. High-level officials spend time and resources to visit other countries for economic or security purposes -- to strengthen the bilateral relationship. Since both approaches feature scarce time and resources to be invested, we expect that Beijing will choose whom to cast the spotlight and to visit strategically. In other words, countries that receive higher state-sponsored media coverage and diplomatic visits are strategically important in the eyes of Beijing. They are in the potential friend circle. While public diplomacy is one way to increase a state's soft power, in the end, it is intangible power and symbolic. Foreign aid, instead, provides tangible and materials support to the countries in need. Hence, we expect China to prioritize giving foreign aid to its "friends" -- countries where China has developed multi-facet relationships through public diplomacy efforts. This rationale leads to our hypotheses:

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

@@

On the one hand, since aid is supposed to have more direct links to China's foreign policy goals, it follows that China will complement its aid giving with visible acts of diplomacy and efforts to increase the salience of aid recipients in foreign audiences. On the other hand, while aid and debt may have different goals, such a tidy distinction may be too simplistic. Perhaps more importantly, some of the market oriented objectives that drive China's global debt might benefit from public displays of diplomacy. On this front, recent research suggests that Beijing uses its debt to ensure access to natural resources that China lacks domestically. As noted above, @dreherEtAl2021 find that Beijing targets more of its loans in resource rich developing countries, a strategy that @dreher_banking_2022 contend is meant to guarantee access to said resources. When Beijing's policy banks provide these loans, developing country governments collateralize their oil or rare minerals, all but assuring access to these resources for Beijing since many of these countries are unable to directly repay the loans[@dreher_banking_2022].

@@

We have made the case that both foreign state-sponsored media and diplomatic visits can be used to sway foreign public opinion in favor of Beijing. By covering developing countries that receive Chinese development financing, *Xinhua* editors can paint a positive picture of Beijing's financing and, in so doing, take steps to promote China's international image. In addition, by sending regular diplomatic missions to developing countries, Beijing is able to strengthen its bilateral relationships with countries in the Global South. Since both approaches feature scarce time and resources, we expect that Beijing will choose on whom to cast the spotlight and to visit strategically.

Most importantly for China's overseas development financing, coverage and diplomatic visits are immediate visible signals of Beijing's priorities. For this reason, Beijing may use both as a way to complement related political objectives it seeks to promote via its financing activities (e.g., its overseas aid and its overseas debt).

To the extent that aid supports Beijing's foreign policy goals, we should expect that aid recipients will be both targets of greater foreign-facing media coverage in *Xinhua* and hosts of a greater number of diplomatic missions from Beijing.

> H1: Developing countries that receive more foreign aid from China will receive more coverage in *Xinhua*.

> H2: Developing countries that receive more foreign aid from China will host more diplomatic missions from China.

The same logic applies to Beijing's use of debt. If loans function in service of political objectives, then countries that owe greater debt to Beijing also will be both targets of greater foreign-facing media coverage in *Xinhua* and hosts of a greater number of diplomatic missions from Beijing.

> H3: Developing countries that owe more debt to China will receive more coverage in *Xinhua*.

> H4: Developing countries that owe more debt to China will host more diplomatic missions from China.

If we can reject the null hypothesis for H1 and H2, but cannot for H3 and H4, this will be consistent with the view that China uses aid---not debt---for political goals [@dreher_banking_2022].
